\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-09 paper/main.tex
u

%% macros
\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
\newcommand{\tname}{BugsInDLLs}
\newcommand{\jax}{JAX}
\newcommand{\torch}{PyTorch}
\newcommand{\tf}{Tensorflow}
\newcommand{\numbugs}{102}

@@

\begin{table}
  \centering
  \label{table:bug-characterization}
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

@@

\section{Related Work}

>>>>

\input{macros}

@@

\begin{table}
  \centering
  \label{table:bug-characterization}
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{l|rrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{r}{build}          &   \multicolumn{1}{r}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

@@

\section{Related Work} 
Defects4J\cite{just2014defects4j}
BugsInPy~\cite{widyasari2020bugsinpy}
Tests4Py~\cite{smytzek2024tests4py}
Denchmark~\cite{kim2021denchmark}
